A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-26 manuscript.Rmd
anontate code chunks with programming language

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts is a matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

<!-- researcher should begin early to enjoy most benefits -->
It can be tempting to leave considerations of reproducibility for when you finish a project.
<!-- weird sentence, I'll leave it as a placeholder-->
However, reproducibility is invaluable for collaboration---including with the version of yourself from a few weeks ago.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you archive reproducibility gradually.
The first step is to organize all files in one folder.
This way, you never lose anything, and you can easily share the files.
<!-- Hands-on: Introducing RProjects-->
RStudio's RProjects facilitate this concept of a project folder.
To create one, click on:

@@

```{r idea-change, echo=FALSE, fig.cap="A screenshot of how a change tracked in Git is represented by GitHub.  ", out.width='100%'}
knitr::include_graphics(idea_change)
```

<!--I am troubled by how we should recomend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

```{r, include=FALSE}
source(here::here("R", "simulation.R"))
```

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis that you plan fit together.
Of course one has to make a lot of educated guesses.
Generally there are of course hundreds of different equal possibilities, but we just care about the worst reasonable settings.
Sticking with our example about machiavilism, we simulate multivariate normal data representing the machiavilism subscale of the short dark triad (SD3).
As a starting point we can use already publishes information.
@Jones2013 report loadings seen in Table \@ref(tab:loadings) and report a gender difference (at the manifest level) depending on the sample between `r min(cohend_jones_paulhus)` and `r max(cohend_jones_paulhus)`.

```{r loadings, echo=FALSE}
knitr::kable(data.frame(Item = 1:9,
                        Loading = loadings_jones_paulhus),
             caption = "Factor loadings from an Exploratory Structrural Equation Model as reported in Jones \\& Paulhus (2013)")
```

It is probably better to assume values that are more pessimistic.
Instead of taking these values as they are we will therefore assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into `lavaan` model syntax:

```{r, results='asis', echo=FALSE}
model_truth <- paste(measurement(
  "MACH",
  paste0("x", 1:9),
  loadings = round(loadings_jones_paulhus * 0.7, 2)
),
intercepts("MACH", list(0, 0.1)),
collapse = "\n", sep = "\n")
cat("``` r",
    model_truth,
    "```",
    sep = "\n")
model <- paste(measurement(
  "MACH",
  paste0("x", 1:9)),
  intercepts("MACH", list(0, "NA")),
  sep = "\n")
```

From which we can simulate data and fit a model to it:

```{r, results='hide'}
data <- lavaan::simulateData(model_truth, "cfa", sample.nobs = c(20000, 20000), meanstructure = TRUE, standardized = TRUE)
fit <- lavaan::cfa(model, data = data, group = "group", meanstructure = TRUE, std.lv = TRUE, group.equal = c("loadings", "intercepts")) 
lavaan::summary(fit)
```

>>>>

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement this concepts are mere matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

<!-- researcher should begin early to enjoy most benefits -->
It can be tempting to leave considerations of reproducibility for when you finish a project.
<!-- weird sentence structure, I'll leave it as a placeholder-->
However, reproducibility is invaluable for collaboration---including with the version of yourself from a few weeks ago.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you archive reproducibility gradually.
The first step is to organize all files in one folder.
This way, you never lose anything, and you can easily share the files.
<!-- Hands-on: Introducing RProjects-->
RStudio's RProjects facilitate this concept of a project folder.
To create one, click on:

@@

```{r idea-change, echo=FALSE, fig.cap="A screenshot of how a change tracked in Git is represented by GitHub.  ", out.width='100%'}
knitr::include_graphics(idea_change)
```
<!--I am troubled by how we should recomend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis that you plan fit together.
